
%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block
%
\documentclass{subfiles}
\begin{document}
\clearpage
\recipient{Resume Viewer}{} % Letter recipient
\date{\today} % Letter date
\opening{Dear Sir or Madam,} % Opening greeting
\closing{Sincerely yours,} % Closing phrase
\enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents

\makelettertitle % Print letter title
%\justify
With a Bachelor’s degree in Information Engineering Technology and hands-on experience using Python languages to create and implement software applications, Confident I will be an asset to your projects and team.
\newline
Enjoy being challenged and engaging with projects that require me to work outside my comfort and knowledge set, as continuing to learn new languages and development techniques are important to me.
\newline
Your listed requirements closely match my background and skills. A few I would like to highlight that would enable me to contribute to your bottom line are:

\begin{itemize}
        \item[$\ast$] Highly skilled in designing, testing, and developing software.
        \item[$\ast$] Managing high performance and scalable Applications.
%        \item[$\ast$] Data Analytics, Data Science, ETL, Python for some ML.
	\item[$\ast$] Certified in MicroServices Design Thinking (SkillSoft), DevOps Foundation (PeopleCert), Data Science (datacamp), 
                        Deep Learning (Udacity), Data Analytics(Udacity).
        \item[$\ast$] Helping and collaborate with team member for self-development and gaining knowledge.
        \item[$\ast$] Thorough understanding of data structures and algorithms.
        \item[$\ast$] Knowledgeable of back-end development best practices.
        \item[$\ast$] Bussiness oriented features to development and production phase.
        \item[$\ast$] Hands-on software troubleshooting experience.
\end{itemize}

I can find myself suitable with your technical requirements, also improving myself in all fields, 
to be aware with cutting Edge technologies and soft skills required/necessary for nowadays market. 
trying to build more suitable environment and career success.

Proven track record of proper documentation for future maintenance and upgrades.
A copy of my \httplink[Summarized resume]{github.com/georgemessiha22/resume/blob/master/George_Messiha_Resume.pdf} attached, 
(\httplink[detailed resume]{github.com/georgemessiha22/resume/blob/master/George_Messiha_detailed_resume.pdf}) 
that details my experience in software development.
\newline
You can reach me anytime via my cell phone or via email.
Thank you for your time and consideration. looking forward to speak with you about the opportunity.

\makeletterclosing % Print letter signature

\newpage

\end{document}
